Transparency in Science

### 2023-05-20 presentation.Rmd
dont use path versions yet

---
background-image: url("images/contribution_path.svg")
background-position: center
background-size: contain

@@

---
background-image: url("images/contribution1_path.svg")
background-position: center
background-size: contain
---
background-image: url("images/contribution2_path.svg")
background-position: center
background-size: contain
---
background-image: url("images/contribution3_path.svg")
background-position: center
background-size: contain
---
background-image: url("images/contribution4_path.svg")
background-position: center
background-size: contain
---
class: middle

>>>>

---
background-image: url("images/contribution.svg")
background-position: center
background-size: contain

@@

---
background-image: url("images/contribution1.svg")
background-position: center
background-size: contain
---
background-image: url("images/contribution2.svg")
background-position: center
background-size: contain
---
background-image: url("images/contribution3.svg")
background-position: center
background-size: contain
---
background-image: url("images/contribution4.svg")
background-position: center
background-size: contain
---
class: middle
